\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-02-05 manuscript/manuscript.tex
precipitation tables

\input{tables/precipitation_pvals}
%\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}

As displayed in Table~\ref{table:precipitation}, using a significance level as 
high as .10 still results in a failed rejection
of the null hypothesis for each of the three tests that the respective 
time series follow the GEV distribution.

>>>>

%\input{tables/precipitation_pvals}
%\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}

The p-value is 0.71 for MDW, 0.13 for LGA, and 0.36 for LAX. Using a 
significance level as 
high as .10 still results in a failed rejection
of the null hypothesis for each of the three tests that the respective 
time series follow the GEV distribution.
